\subsection{Theory: Isotopic Cloud Microphysics}

\begin{tasks}
    \taskitem
    {Isotope-specific governing equations and mixed-phase Bolin number.
    Develop a unified mathematical framework describing isotopic mass transfer
    among vapour, liquid, and ice phases, including equilibrium and kinetic
    fractionation and extension of the Bolin number.}
    {task:T1}
    \textbf{Deliverable}: Mathematical formulation of mixed-phase isotope cloud microphysics.

    \taskitem
    {Reduced-order models. Identify limiting regimes including equilibrium,
    Rayleigh distillation, and diffusion-limited growth.}
    {task:T2}
    \textbf{Deliverable}: Reduced models for closure analysis.

    \taskitem
    {Sensitivity and uncertainty analysis of isotopic evolution.}
    {task:T3}
    \textbf{Deliverable}: Sensitivity maps and uncertainty framework.
\end{tasks}


\subsection{Numerical Framework: Particle-Based Implementation}

\begin{tasks}
    \taskitem
    {Box, Parcel, and One-Column isotope-enabled simulations with validation.}
    {task:T4}
    \textbf{Deliverable}: Jupyter notebook collection.
    
    \taskitem
    {Ice-phase isotope microphysics and multi-isotopologue (\ce{HDO}, \ce{H2^{18}O}, \ce{H2^{17}O}).}
    {task:T5}
    \textbf{Deliverable}: Ice-phase module with unit tests.
    
    \taskitem
    {Minimal isotope-enabled cloud model for closure studies.}
    {task:T6}
    \textbf{Deliverable}: Open-source model with documentation.
\end{tasks}

\subsection{Validation and Closure Assessment}

\begin{tasks}
    \taskitem
    {Preparation of observational and laboratory datasets with uncertainty characterization.}
    {task:T7}
    \textbf{Deliverable}: Data-processing pipeline and emulator.
    
    \taskitem
    {Data--model comparison using quantitative diagnostics.}
    {task:T8}
    \textbf{Deliverable}: Model performance metrics.
    
    \taskitem
    {Assessment of isotopic closure and required physical constraints.}
    {task:T9}
    \textbf{Deliverable}: Closure framework (Q1–Q4).
\end{tasks}


